### 2024-08-10 paper.tex
more on dimension

@@

\[\sum_i \sum_j d_{ij} -\max(0, \max_j [d_{ij} - q_j]).\]

>>>>

Then if \(A_{X, a, b}\) is nilpotent, we must have \(q_{i_0} \geq j_0\).
So we may as well set \(q_{i_0} := q_{i_0} - j_0\).

@@

\[\sum_i \left[\sum_j d_{ij} -\max(0, \max_j [d_{ij} - q_j])\right] = \sum_{ij} d_{ij} - \sum_i \max(0, \max_j[d_{ij} - q_j]).\]
When \(i \neq i_0\), then \(d_{ii} = \lambda_i \geq q_i\), and therefore \(\max(0, \max_j [d_{ij} - q_j]) = \max_j [d_{ij} - q_j]\).
When \(i = i_0\), then \(d_{ii} = \lambda_i - j_0 \geq q_{i_0}\).
So, we can simplify the above expression:
\[\sum_{ij} d_{ij} - \sum_i \max_j [d_{ij} - q_j].\]
Note that \(\max_j [d_{ij} - q_j] = \max_j [\min(p_i + q_i, p_j + q_j) - q_j]\).
This thing being maximized equals \(\min(p_i + q_i - q_j, p_j)\).
It would be really helpful if I could simplify this to \(p_j\) or something.
I don't think so, though.
